SMT-Boosted Security Types for Low-Level MPC

### 2025-01-29 esop25/camera-ready/examples.tex
checkpoint

\section{Extended Examples}
\label{section-examples}

@@

\subsection{Confidentiality Examples}

@@

\subsection{Integrity Examples}

\input{bdoz}

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{\mesg{w}}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{\mesg{w}}$. The preconditions
of $\ttt{open}$ specify the authentication requirements.

The $\ttt{sum}$ function implements an addition gate. This is
non-interactive-- each party just sums its local shares
of the two values. The pre- and postcondition annotations
on $\ttt{sum}$ express the additive homomorphism associated
with this encryption scheme-- the sum of MACs of the input
shares is a valid MAC for the output share on each client,
which can be checked using the sum of keys of the input shares.

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given these global preconditions, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$,
which type checks.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc.

%, and $\eqspre$
%subsumes the following constraints for the $a,b,c$ values of gate
%$\ttt{"g1"}$.  {\footnotesize$$
%\begin{array}{l}
%\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
%\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
%\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
%\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{1} \eop \\
%\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
%\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
%\end{array}
%$$}

The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult},
%where we present just client 1's side of the
%protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
%a small variation-- refer to
%\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
%details).
%We could call this function on input secrets
%$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
%$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
%this gate internally in a circuit.
%
As for $\ttt{sum}$, the preconditions of $\ttt{mult}$ express
the expected MAC properties of input shares, as well as the
expected Beaver Triple property, and its postcondition
fexpresses the semi-homomorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. Finally, the
postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little SMT overhead
due to compositional verification, once their pre- and postconditions
are verified by type checking.

%%%%%%%%%%%%%%%%%%
%%% ARCHIVAL BELOW
%%%%%%%%%%%%%%%%%%
\begin{comment}
\begin{verbatimtab}
andtableygc(g,x,y)
{
   let table = (~r[g],~r[g],~r[g],r[g])
   in permute4(r[x],r[y],table)
}

m[x]@1 := s2(s[x],r[x],~r[x])@2;
m[x]@1 as s[x]@2 xor r[x]@2;

// m[x]@1 : { c(r[x]@2, { s[x]@2 }) }

m[y]@1 := OT(s[y]@1,r[y],~r[y])@2;
m[y]@1 as s[y]@1 xor r[y]@2;

// m[y]@1 : { c(r[y]@2, { s[y]@1 }) }

m[ag]@1 := OT4(m[x]@1, m[y]@1, andtable(ag,r[x],r[y]))@2;
m[ag]@1 as  ~((r[x]@2 = m[x]@1) and (r[y]@2 = m[y]@1)) xor r[ag]@2;

// m[ag]@1 : { c(r[ag]@2, {r[x]@2, r[y]@2, m[x]@1,  m[y]@1} }

p[o] := OT2(m[ag]@1, perm2(r[ag],(false,true)))@2

// p[o] : { c(r[ag]@2, {r[x]@2, r[y]@2,  m[x]@1,  m[y]@1}), r[ag]@2  }

out@1 := p[o]@1

// out@1 == s[x] and s[y]
\end{verbatimtab}

\begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i1;
      m[in]@i1 := r[in]@i1
    }

    andtablegmw(x, y, z) {
      let r11 = r[z] xor (m[x] xor true) and (m[y] xor true) in
      let r10 = r[z] xor (m[x] xor true) and (m[y] xor false) in
      let r01 = r[z] xor (m[x] xor false) and (m[y] xor true) in
      let r00 = r[z] xor (m[x] xor false) and (m[y] xor false) in
      { row1 = r11; row2 = r10; row3 = r01; row4 = r00 }
    }

    andgmw(z, x, y) {
      let table = andtablegmw(x,y,z) in
      m[z]@2 := OT4(m[x],m[y],table,2,1);
      m[z]@2 as ~((m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2)) xor r[z]@1);
      m[z]@1 := r[z]@1
    }

    // and gate correctness postcondition
    {} andgmw { m[z]@1 xor m[z]@2 == (m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2) }

    // and gate type
    andgmw :
     Pi z,x,y .
     {}
     { { r[z]@1 },
       (m[z]@1 : { r[z]@1 }; m[z]@2 : {c(r[z]@1, { m[x]@1, m[x]@2, m[y]@1, m[y]@2 })} ),
       m[z]@1 xor m[z]@2 == (m[x]@1 xor m[x]@2) and (m[y]@1 xor m[y]@2)}

    xorgmw(z, x, y) {
      m[z]@1 := (m[x] xor m[y])@1; m[z]@2 := (m[x] xor m[y])@2;
    }

    decodegmw(z) {
      p["1"] := m[z]@1; p["2"] := m[z]@2;
      out@1 := (p["1"] xor p["2"])@1;
      out@2 := (p["1"] xor p["2"])@2
    }

    prot() {
      encodegmw("x",2,1);
      encodegmw("y",2,1);
      encodegmw("z",1,2);
      andgmw("g1","x","z");
      xorgmw("g2","g1","y");
      decodegmw("g2")
    }

    {} prot { out@1 == (s["x"]@1 and s["z"]@2) xor s["y"]@1 }
\end{verbatimtab}

\subsection{Integrity Examples}

\begin{verbatimtab}
  secopen(w1,w2,w3,i1,i2) {
      pre(m[w1++"m"]@i2 == m[w1++"k"]@i1 + (m["delta"]@i1 * m[w1++"s"]@i2 /\
          m[w1++"m"]@i2 == m[w1++"k"]@i1 + (m["delta"]@i1 * m[w1++"s"]@i2));
      let locsum =  macsum(macshare(w1), macshare(w2)) in
      m[w3++"s"]@i1 := (locsum.share)@i2;
      m[w3++"m"]@i1 := (locsum.mac)@i2;
      auth(m[w3++"s"],m[w3++"m"],mack(w1) + mack(w2),i1);
      m[w3]@i1 := (m[w3++"s"] + (locsum.share))@i1
  }

  _open(x,i1,i2){
    m[x++"exts"]@i1 := m[x++"s"]@i2;
    m[x++"extm"]@i1 := m[x++"m"]@i2;
    assert(m[x++"extm"] == m[x++"k"] + (m["delta"] * m[x++"exts"]));
    m[x]@i1 := (m[x++"exts"] + m[x++"s"])@i2
  }`

  _sum(z, x, y,i1,i2) {
      pre(m[x++"m"]@i2 == m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2 /\
          m[y++"m"]@i2 == m[y++"k"]@i1 + (m["delta"]@i1 * m[y++"s"]@i2));
      m[z++"s"]@i2 := (m[x++"s"] + m[y++"s"])@i2;
      m[z++"m"]@i2 := (m[x++"m"] + m[y++"m"])@i2;
      m[z++"k"]@i1 := (m[x++"k"] + m[y++"k"])@i1;
      post(m[z++"m"]@i2 == m[z++"k"]@i1 + (m["delta"]@i1 * m[z++"s"]@i2)
  }

  sum(z,x,y) { _sum(z,x,y,1,2);_sum(z,x,y,2,1) }

  open(x) { _open(x,1,2); _open(x,2,1) }

  sum("a","x","d");
  open("d");
  sum("b","y","e");
  open("e");
  let xys =
      macsum(macctimes(macshare("b"), m["d"]),
             macsum(macctimes(macshare("a"), m["e"]),
                    macshare("c")))
  let xyk = mack("b") * m["d"] + mack("a") * m["e"] + mack("c")

  secopen("a","x","d",1,2);
    secopen("a","x","d",2,1);
    secopen("b","y","e",1,2);
    secopen("b","y","e",2,1);
    let xys =
      macsum(macctimes(macshare("b"), m["d"]),
             macsum(macctimes(macshare("a"), m["e"]),
                    macshare("c")))
    in
    let xyk = mack("b") * m["d"] + mack("d") * m["d"] + mack("c")               
    in
    secreveal(xys,xyk,"1",1,2);
    secreveal(maccsum(xys,m["d"] * m["e"]),
              xyk - m["d"] * m["e"],
              "2",2,1);
    out@1 := (p[1] + p[2])@1;
    out@2 := (p[1] + p[2])@2;
\end{verbatimtab}

\end{comment}

>>>>

\section{Extended Example: GMW}
\label{section-examples}

@@

@@
